Title Goes Here

### 2020-03-30 analysis/paper/paper.Rmd
SYG6 site
This is what I did during our last meeting on Friday

@@

ggbiplot(PCA, obs.scale = 1, var.scale = 1,          ellipse = TRUE, circle = TRUE)+
scale_color_discrete (name = '') +
  theme(legend.direction = 'horizontal', legend.position = 'top')

>>>>

#list of all attributes
df <- data.frame(ML, BL, TL, SL, MW, TW, SW, files)
library(tidyverse)
df_sitename <- df %>% 
  mutate(files = str_remove_all(files, "A_|1|2|.tps")) %>% 
  separate(files, into = c("sitename", "files"), sep = "_") %>% 
  select(-files)

#list of all attributes without ID
DF <- df[,1:7]

@@

autoplot(prcomp(DF), data = df_sitename, colour = 'sitename')

ggbiplot(PCA, obs.scale = 1, var.scale = 1,          ellipse = TRUE, circle = TRUE)+
scale_color_discrete (name = '') + groups (df$files)
  theme(legend.direction = 'horizontal', legend.position = 'top')
